\documentclass[conference]{IEEEtran}

\ifCLASSINFOpdf
\else
\fi
\hyphenation{op-tical net-works semi-conduc-tor}

\input{00setup/preambleIEEE.tex}
\input{00setup/Tikz.tex}

\begin{document}

\title{Active Noise Control of Speech in Headphones using Linear Prediction}

\author{\IEEEauthorblockN{Christian Claumarch, Kasper Kiis Jensen, Maxime Démurger, \\Mikkel Krogh Simonsen, Oliver Palmhøj Jokumsen}
\IEEEauthorblockA{Aalborg University - Acoustics and Audio Technology - 16gr761 - Fall 2016 \\
\{cclaum16, kkje13, mdemur16, mksi13, ojokum12\}@student.aau.dk}
}

\maketitle

\begin{abstract}
Active Noise Control (ANC) is a widely used technique in consumer headphones for attenuating noise. ANC is useful for attenuation of periodic noise e.g. machinery but has limited ability to attenuate quasiperiodic noise e.g. speech (50 Hz -- 4000 Hz). This paper therefore focuses on improving attenuation of speech. Feedforward ANC systems are widely used, where an FIR-filter is adapted by a Filtered-$x$ Least Mean Squares (FXLMS)-algorithm. The main problem when implementing ANC is delays in converters. A tested $\Sigma\Delta$-converter has a delay of 225 $\mu$s -- 900 $\mu$s. A Linear Prediction (LP) method combined with multirate processing is proposed to compensate for the introduced conversion delays. A signal sampled at 192 $k$Hz decimated to 48 $k$Hz requires prediction of 10 samples.   Cascaded Wiener filtering is therefore used to predict 10 samples $\approx$ 225 $\mu$s at 48 $k$Hz. 
\\\\
The combined feedforward LP FXLMS system is found by simulation to have a 36 dB larger attenuation at 1600 Hz than the system without LP. The combined system yields a high attenuation for all frequencies in the speech area. No real time implementation is attempted because the computational cost of the proposed LP is >50,000 instructions per sample. %This needs to be reduced for a real time implementation to be feasible.  	
	
%Active Noise Control (ANC) is a widely used technique in consumer headphones for attenuating noise. ANC is good at attenuating periodic noise e.g. machinery but has limited ability to attenuate quasiperioc noise e.g. speech (50 Hz -- 4000 Hz). This paper therefore focusses on attenuation of speech. A widely used feedforward ANC system which uses an FIR-filter adapted by an Filtered-$x$ Least Mean Square (FXLMS)-algorithm is adopted. However using a $\Sigma\Delta$-converter which has a delay of 225 $\mu$s -- 900 $\mu$s decreases the attenuation of the used ANC system. A Linear Prediction (LP) method combined with multirate processing is proposed to compensate for the introduced conversion delay. Cascaded Wiener filtering is used to predict 10 samples ahead corresponding to 225 $\mu$s at 48 $k$Hz. A signal sampled at 192 $k$Hz decimated to 48 $k$Hz requires prediction of 10 samples.  
%\\\\
%The combined LP FXLMS system is found by simulation to have a 36 dB larger attenuation at 1600 Hz than the system without LP. The combined system yields a high attenuation for all frequencies in the speech area. No real time implementation is attempted because the computation cost of the LP is >15,000 instructions per sample. %This needs to be reduced for a real time implementation to be feasible.           
\end{abstract}

\IEEEpeerreviewmaketitle

\input{1Article/Introduction.tex}
\input{1Article/Methods.tex}
\input{1Article/Results.tex}
\input{1Article/Conclusion.tex}


\bibliography{00setup/mybib}




% that's all folks
\end{document}


