%% Introduction


\section{Introduction}
\begin{itemize}
\item WHY is the topic of interest? 
\item WHAT (1) is the background on the previous solutions, if any?
\item WHAT (2) is the background on potential solutions?
\item WHAT (3) was attempted in the present effort?
\item WHAT (4) will be presented in this paper?
\end{itemize}

\lettrine[lines=2]{A}{ctive} Noise Control (ANC) is becoming a widely used technique to attenuate noise in consumer headphones. One of the limiting factors in ANC is the upper frequency which is attenuated, therefore it is of interest to examine why performance decreases with increased frequency and how to extend bandwidth.  

The general solutions in ANC are described thoroughly by Hansen et al. \cite{Hansen2}\cite{Hansen}. 



 The scope of this paper is not to derive a new ANC algorithm, but rather to expand the existing FXLMS algorithm by prediction. The goal of this modification is to achieve increased performanec, especially at higher frequencies.\\
The application of the system is cancellation of speech in a call centre. The choice of a specific use case allows the frequency range and signal type of interest to be defined before designing the system. Call centres is an especially interesting environment for an ANC system, because the unwanted noise and the wanted signal have the same  characteristics as they are both speech. \\
The paper is split into three parts. The first part examines the demands for an ANC system to be used in a call centre. The second part discus the algorithm used and shows preliminary results from simulations. The third part describes the real time implementation of the algorithm and verifies the performance of the ANC system.  




\lettrine[lines=2]{A}{ctive} Noise Control (ANC) is a field of study, where a lot of algorithms are already known. The scope of this paper is not to derive a new ANC algorithm, but rather to expand the existing FXLMS algorithm by prediction. The goal of this modification is to achieve increased performanec, especially at higher frequencies.\\
The application of the system is cancellation of speech in a call centre. The choice of a specific use case allows the frequency range and signal type of interest to be defined before designing the system. Call centres is an especially interesting environment for an ANC system, because the unwanted noise and the wanted signal have the same  characteristics as they are both speech. \\
The paper is split into three parts. The first part examines the demands for an ANC system to be used in a call centre. The second part discus the algorithm used and shows preliminary results from simulations. The third part describes the real time implementation of the algorithm and verifies the performance of the ANC system.  




%\lettrine[lines=2]{A}{ctive} Noise Control (ANC) is a field of study, where a lot of algorithms are already known. \todo[inline]{$MENTION A FEW$} The scope of this paper is not to derive a new ANC algorithm, but rather to use an existing algorithm in a practical application. The application is cancellation of speech in a call centre The choice of a specific use case allows the frequency range and signal type of interest to be defined before designing the system. Call centres is an especially interesting environment for an ANC system, because the unwanted noise and the wanted signal have the same  characteristics as they are both speech. \\
%The paper is split into three parts. The first part examines the demands for an ANC system to be used in a call centre. The second part discus the algorithm used and shows preliminary results from simulations. The third part describes the real time implementation of the algorithm and verifies the performance of the ANC system.  