% This file was converted to LaTeX by Writer2LaTeX ver. 1.2
% see http://writer2latex.sourceforge.net for more info
\documentclass[a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage[top=2.54cm,bottom=2.54cm,left=2.54cm,right=2.54cm,nohead,nofoot]{geometry}
\usepackage{array}
\usepackage{caption}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue}
% Footnote rule
%\setlength{\skip\footins}{0.119cm}
%\renewcommand\footnoterule{\vspace*{-0.018cm}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.018cm}}\vspace*{0.101cm}}
\title{}
\begin{document}
\[%\clearpage\clearpage\setcounter{page}{1}{\centering\color{black}
%%%{\centering
%%%\subsection*{PREPARATION OF ABSTRACTS FOR SEMCON IN SCIENTIFIC COMMUNICATION}}
%%%
{\centering
\textit{Jimmy J. Nielsen*, John Doe**}
\par}
{\centering
\textbf{Group VIPXYZ}
\par}


\bigskip

\paragraph{Introduction}
This sample abstract provides instructions and the basic guide-lines for preparing an abstract for the Student Conference in Scientific Communication (SEMCON) to be held in Aalborg, Denmark. The abstracts must contain no more than 400 words (excl. references) and no more than 1 page. The title of the abstract is followed by the list of authors in alphabetic order. Below is given the affiliation of the authors in terms of the group number. The name of the presenter of the poster must be marked with {\textquotedbl}*{\textquotedbl} and the name of the person giving the oral presentation with {\textquotedbl}**{\textquotedbl}.

\paragraph{Methods and Proposals}
The text was checked for spelling-errors. Abbreviations and acronyms were always defined the first time they were used in the text. The following style was used for references and citations [1]. Multiple references were numbered consecutively in square brackets [1,2]. The sentence punctuation followed the brackets [2]. Avoid the use of {\textquotedbl}Ref. [2]{\textquotedbl} or {\textquotedbl}reference [2]{\textquotedbl}, except at the beginning of a sentence. The list of references was formatted as follows: List of authors. Title of paper with first word capitalized, name of journal, year, volume number, page numbers separated by a hyphen [1]. For references to books use the style as in [2].


\paragraph{Results}
The abstracts should be submitted in a pdf file adhering exactly to this format. Please send it to Tatiana K. Madsen, \href{mailto:tatiana@es.aau.dk}{tatiana@es.aau.dk}. State clearly in the subject [SEMCON] and the group number. All abstracts should be in accordance with the instructions.

\paragraph{Discussion}
An online book of abstracts will be prepared containing all abstracts for SEMCON including a specific time schedule for the conference. This was organized by the conference secretariat. The abstract book allows a better communication between participants during the conference. Please be aware of the tight schedule for the SEMCON, which does not allow for computer-projector problems. For each session, the presenters should upload their presentations to the designated computer in the presentation room 15 min before the session start. In case of technical problems, it is recommended to also send your presentation to Tatiana Madsen. Only presentations in Powerpoint (.ppt, pptx) or PDF (.pdf) formats are accepted.


\paragraph{References}

\begin{description}
\item{[1]} Haugland MK, Hoffer JA. Sensory nerve signals obtained from cuff electrodes during functional electrical stimulation of nearby muscles. IEEE Trans. Rehab. Eng. 1994; 2: 37-40.

\item{[2]} Jacobs IS, Bean CP. Fine particles, thin films and exchange anisotropy. In: Rado GT, Suhl H (eds.), Magnetism (vol. 3). New York NY: Academic Press, 1963: 271-350.
\end{description}
\end{document}