\section{Automation of tests in Simulink} \label{sec:SimulinkAuto}
This sections describes an automated test setup used with simulations to run the same simulation multiple times with different parameters 

\subsection{variables}
A lot of variables, are declared in the simulations and they are not all described here. The ones described are only the tunable parameters, that should be set in the prediction problem that should be solved. 
\begin{lstlisting} [language=MATLAB]
N; 				%is the frame length used as memory in the prediction and the prediction order
overlap;		%is the overlap in the buffer "O"
prediction; 	%is how far the algorithm should predict "P"
fs; 			%is the sample frequency of the input signal 
w=hamming(N)	% could be replaced by other window functions
M;				% is equal to N in all cases
\end{lstlisting}

\subsection{Test setup.}
It might be required to run a simulation with a lot of different parameters. Rather than going for a random trial and error approach a systematic variation approach was chosen. If a person should control the simulations manually a lot of time would be spent, waiting for the algorithm to run. Therefore an automated test setup was constructed. The automation consists of 4 parts. 
\begin{enumerate}
	\item The prediction simulink
	\item An initiation 
	\item Saving data
	\item A script controlling parameters 
\end{enumerate}  

Below an example of the 3 controlling scripts are shown. The  scripts should be modified to run the simulator using the desired combination of parameters.

\textbf{Init.m}\\
If a variable is not controlled in "RunSim.m" it should be set here. 
\begin{lstlisting} [language=MATLAB]
fs = 48000;
ts = 1/fs; 
% Predictor 
% N = 50; %Frame
% M = N;   %Coefficients
% overlap = 0; %updaterate
% prediction = 1; % How far should the prediction be
w = hamming(N); 
% w = rectwin(N);
%w = barnwell(N,0.98);
% w = fliplr(w);
\end{lstlisting}

\textbf{SaveData.m}\\
It is possible to modify the save function to store all variables, including the calculated audio. This however results in approximately 5 $M$B of data pr simulation.  
\begin{lstlisting} [language=MATLAB]
	PG=10*log10(var(Ref)/var(ErrorSig));
	
	fname = sprintf(['fs' num2str(fs ) '_N' num2str(N) '_O' num2str(overlap) ...              '_M' num2str(M) '_P' num2str((prediction)) '.mat']);
	
	save(fname,'fs','N','overlap','M','prediction','PG');
\end{lstlisting}

\textbf{RunSim.m}
\begin{lstlisting} [language=MATLAB]
	clear 
	prediction=10;
	
	for N=100:100:3000
		M=N;
		for overlap=0:100:N-100
			sim('Predictora.slx')
			disp(['overlap=' num2str(overlap) 'done'])
		end
		disp(['N=' num2str(N) ' done'])
	end
	
	disp('I am done')	
\end{lstlisting}


Afterwards the script "loadData.m" can be used to structure the saved .mat  files in a single matrix.\\
\textbf{LoadData.m}
\begin{lstlisting} [language=MATLAB]
	clear
	close all
	fs=48000;
	prediction=10;
	counter=0;
	
	for N=100:100:3000
	M=N;
		for overlap=0:100:N-100
			fname = sprintf(['fs' num2str(fs) '_N' num2str(N) '_O' num2str(overlap) '_M' num2str(M) '_P' num2str((prediction)) '.mat']);
			load(fname)
			counter=counter+1;
			result(counter,:)=[fs N overlap M prediction PG]; 
		end
	end
	
	disp('I am done')
\end{lstlisting}
