\section{Measuring A Transfer Function}\label{Sec:MeasATransFunc}
This section describes the mathematics used in the measurement system. The system can estimate a transfer function H(f) of a system using a reference signal containing all frequencies of interest, typically  a logarithmic sine sweep. The user should ensure that the entire reference signal is recorded. This probably requires some zero padding of the time signal before playback. For further documentation, the reader should consult \cite{TutorialMeasurementPowerSpectra}.
\subsection{Transfer functions in general}
The general way of expressing a transfer function in frequency domain is:
\begin{equation}
H(f)=\frac{Y(f)}{X(f)}
\label{Eq:TranferFunction}
\end{equation}
Where $X(f)$ is the Fourier transform of the input signal and $Y(f)$ is the Fourier transform of the the output.  

\subsection{Transfer functions two port system}
In a typical set-up you want to measure the transfer function of a single device, e.g. a loudspeaker. An amplifier is needed to drive the loudspeaker, but the amplifiers transfer function is not of interest. A two port system allows you to use a measured signal, from somewhere in the signal chain, as a reference. 
\begin{equation}
H(f)=\frac{Y(f)}{X(f)}=\frac{\mathscr{F}(y(t))\times\mathscr{F}^{\ast}(x(t))}{\mathscr{F}(x(t))\times\mathscr{F}^{\ast}(x(t))}
\label{Eq:TranferFunctionTwoPort}
\end{equation}
Where $\star $ denotes the cross-correlation and $\ast $ denotes the convolution, and 
 $X(f)$ is the auto-spectrum of the reference signal and $Y(f)$ cross-spectrum of the reference signal and the measured signal. Found by auto- and cross correlation respectively.\\
$x(t)$ and $y(t)$ are measured in time domain and to obtain the cross-spectrum and auto-spectrum, $X(f)$ and $Y(f)$ are calculated.
%\begin{equation}
%Y(f)=\mathscr{F}(y(t))\times\mathscr{F}^{\ast}(x(t)) \text{ \& } X(f)=\mathscr{F}(x(t))\times\mathscr{F}^{\ast}(x(t))
%\label{Eq:cross-spectrum}
%\end{equation}
Where $\times$ denotes bin-wise multiplication and $^{\ast}$ denotes the complex conjugate. \\
From equation \ref{Eq:TranferFunction} %and \ref{Eq:cross-spectrum} 
you can find $H(f)$. Taking the inverse Fourier transform of that will give the impulse response of the system. 
\begin{equation}
H(f) = \frac{Y(f)}{X(f)} \xrightarrow{\mathscr{F}^{-1}} h(t)
\label{Eq:Impulseresponse}
\end{equation} 

\subsection{Cross-correlation method}
The mathematics described above can be converted to time domain, and yield the same result. The choice of method is a matter of convenience. If the Fourier transform of the signals are all ready known the above method is easily calculated. On the other hand if the cross-correlation between $y(t)$ and $x(t)$ is already known the method below might be more efficient
\begin{equation}
H(f)=\dfrac{\mathscr{F}(y(t)\star x(t))} {\mathscr{F}(x(t)\star x(t))}=
\dfrac{\mathscr{F}(y(t)\ast x(-t))} {\mathscr{F}(x(t)\ast x(-t))}
\label{Eq:Xcorr method}
\end{equation}  
 %The deconvolution should be made as a division in frequency domain as this is more robust towards noise in the system. 
 
 \subsection{Matlab function}
 Here a function that can be used to find the transfer function is given. The return value is the response in frequency domain. If an impulse response is take the inverse Fourier transform of the return value. 
 \begin{lstlisting}[language=MATLAB, caption=getTrans.m]
function [ res ] = getTrans( sig,ref )
	res=(fft(sig).*conj(fft(ref)))./(fft(ref).*conj(fft(ref)));
end
 \end{lstlisting} 
